\bf Supplementary Material: Comparing the Power of Plot Designs to Reveal Correlation

### 2016-01-13 paper/paper.Rnw
Few more fixes

#sasdata <- select(full.sub, rabs, n, alpha, rsgn, smoothed, design, subj_id, weights, correct, log_time)
#sasadata <- mutate(sasdata, rabs = as.numeric(rabs),
#                   subj_id = as.numeric(subj_id)
#                   design = ifelse(design=="Scatterplot", 1, 0))
#write.csv(subsetted, "sas/sasdata.csv", row.names = FALSE)
##The code that is exported to fit the model into SAS, see sas/model fit.sas

# data.frame(expand.grid(rabs=rabs, t=t, alpha=log(.05/0.95), rsgn=c(0,1),
#                                      smoothed=c(0,1), design=c(0,1),
#                                      subj_id=full.sub$subj_id))
#pred <- subset(pred, smoothed==0 | smoothed == 1 & t ==48 | smoothed ==1 & t ==96)
#write.csv(pred, "sas/predgrid.csv", row.names=FALSE) # these lines are done, but its a large file so commented out for knitr
#Code exported to SAS to predict new values

>>>>

#sasdata <- select(full.sub, rabs, n, alpha, rsgn, smoothed, design, subj_id, weights, correct, log_time)
#sasadata <- mutate(sasdata, rabs = as.numeric(rabs),
#                   subj_id = as.numeric(subj_id),
#                   design = ifelse(design=="Scatterplot", 1, 0))
#write.csv(sasdata, "sas/sasdata.csv", row.names = FALSE)
#The code that is exported to fit the model into SAS, see sas/model fit.sas

#pred <- data.frame(expand.grid(rabs=seq(0, 0.9, 0.01), t=c(12, 24, 48, 96), alpha=log(.05/0.95), rsgn=c(0,1),
#                                      smoothed=c(0,1), design=c(0,1),
#                                      subj_id=1:160))
#pred <- subset(pred, smoothed==0 | smoothed == 1 & t ==48 | smoothed ==1 & t ==96)
#write.csv(pred, "sas/predgrid.csv", row.names=FALSE) # these lines are done, but its a large file so commented out for knitr
#Code exported to SAS to predict new values

### 2016-01-13 paper/supplementary.Rnw
Few more fixes

\title{\bf Supplementary Material: Comparing the Power of Plot Designs to Reveal Correlation

@@

\begin{figure}[htbp]
\centering
<<map, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
location <- read.csv("location.csv")
map.dat <- map_data("world")
ggplot() + geom_polygon(aes(long,lat, group=group), fill="grey65", data=map.dat) + theme_bw() +
  geom_point(data=location, aes(x=lon, y=lat, colour= "blue")) +scale_colour_manual(values=c("#FF5500", "#00FFFF")) + theme(aspect.ratio = 0.67, axis.text=element_blank(), axis.title=element_blank(), legend.position="none")
@
\caption{The location of the recruited subjects. The majority reside in North America but some are spread around other countries in Central America, Europe and Asia.}
\label{map}
\end{figure}

@@

\begin{figure}[htbp]
\centering
<<choices, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
full$choice_reason <-sapply(strsplit(as.character(unlist(full$choice_reason)), "[^0-9]+"), "[[", 1)
ggplot(data=full.sub) + geom_bar(aes(x=choice_reason))
choice <- full %>% transform(choice_reason= strsplit(as.character(choice_reason), "")) %>% unnest(choice_reason)
choice$rsgn <- factor(choice$rsgn, labels=c("r -","r +"))
choice$correct <- factor(choice$correct, labels=c("Did not detect", "Detected"))
ggplot(data=choice, aes(x=choice_reason, fill=correct)) + geom_bar() + facet_grid(design~rsgn) +
  theme(legend.position="bottom", axis.title=element_blank()) + scale_fill_discrete(name="True Plot")
@
\caption{Reasons given for plot selection}
\label{reasons}
\end{figure}

@@

\begin{table}[htp]
\caption{Number of selections per lineup evaluation. The subject with the most selections is reported.}
\label{tabattempts}
<<tabattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
attempts <- summarise(group_by(full.sub, subj_id, pic_id), attempts = max(attempts))
attempts.table <- data.frame(table(attempts$attempts))
attempts.table$most <- c(0,0,0,5,3,1,1)
colnames(attempts.table) <- c("Selections", "Whole Sample", "Subject 123")
kable(attempts.table, format="latex")
@
\end{table}

\begin{figure}[htbp]
\centering
<<multiattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
ggplot(data=attempts) + geom_bar(aes(x=as.factor(attempts))) + labs(x="Number of selections", y=NULL)
@
\caption{Histogram of table~\ref{tabattempts}}
\label{attemptshist}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<random, dependson='powermodel', fig.height=4, fig.width=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
randomeffects <- summarise(group_by(prediction, subj_id), re=unique(diff))
ggplot(data=randomeffects) + geom_histogram(aes(x=re, y=..density..), binwidth=0.08) + xlab("Random Effects") + ylab(NULL)
@
    \caption{Histograms of estimated subject random effects, $\hat{\gamma}$. They appear to be normally distributed with mean zero.}
  \label{random}
\end{figure}

>>>>

\title{\bf Supplementary Material: Comparing the Power of Plot Designs to Reveal Correlation}

@@

\begin{figure}[htbp]
\centering
<<map, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE, fig.height=3>>=
location <- read.csv("location.csv")
map.dat <- map_data("world")
ggplot() + geom_polygon(aes(long,lat, group=group), fill="grey65", data=map.dat) + theme_bw() +
  geom_point(data=location, aes(x=lon, y=lat, colour= "blue")) +scale_colour_manual(values=c("#FF5500", "#00FFFF")) + theme(aspect.ratio = 0.67, axis.text=element_blank(), axis.title=element_blank(), legend.position="none")
@
\caption{The location of the recruited subjects. The majority reside in North America but some are spread around other countries in Central America, Europe and Asia.}
\label{map}
\end{figure}

@@

\begin{figure}[htbp]
\centering
<<choices, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
full$choice_reason <-sapply(strsplit(as.character(unlist(full$choice_reason)), "[^0-9]+"), "[[", 1)
choice <- full %>% transform(choice_reason= strsplit(as.character(choice_reason), "")) %>% unnest(choice_reason)
choice$rsgn <- factor(choice$rsgn, labels=c("r -","r +"))
choice$correct <- factor(choice$correct, labels=c("Did not detect", "Detected"))
ggplot(data=choice, aes(x=choice_reason, fill=correct)) + geom_bar() + facet_grid(design~rsgn) +
  theme(legend.position="bottom", axis.title=element_blank()) + scale_fill_discrete(name="True Plot")
@
\caption{Reasons given for plot selection}
\label{reasons}
\end{figure}

@@

\begin{table}[htbp]
\caption{Number of selections per lineup evaluation. The subject with the most selections is reported.}
\label{table}
<<tabattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
attempts <- summarise(group_by(full.sub, subj_id, pic_id), attempts = max(attempts))
attempts.table <- data.frame(table(attempts$attempts))
attempts.table$most <- c(0,0,0,5,3,1,1)
colnames(attempts.table) <- c("Selections", "Whole Sample", "Subject 123")
kable(attempts.table, format="latex")
@
\end{table}

\begin{figure}[htbp]
\centering
<<multiattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
ggplot(data=attempts) + geom_bar(aes(x=as.factor(attempts))) + labs(x="Number of selections", y=NULL)
@
\caption{Histogram of table~\ref{table}}
\label{attemptshist}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<random, dependson='setup', fig.height=4, fig.width=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
randomeffects <- summarise(group_by(prediction, subj_id), re=unique(diff))
ggplot(data=randomeffects) + geom_histogram(aes(x=re, y=..density..), binwidth=0.08) + xlab("Random Effects") + ylab(NULL)
@
    \caption{Histograms of estimated subject random effects, $\hat{\gamma}$. They appear to be normally distributed with mean zero.}
  \label{random}
\end{figure}
